### 2019-11-20 thesis.tex
more discussion

Above, on the left-hand side, the differential vector operators $\nabla_{\bf r}$
and $\nabla_{\bf v}$ represent, respectively, the gradients in ($x,y,z$) space
and ($v_x, v_y,v_z$) velocity coordinates. The quantity ${\bf F}$ is the acting
force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
$\alpha$, which, in a fully ionized plasma, can assume two values: electrons
$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
variation of the velocity distribution function due to collisional interactions
between the system's particles.

For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, $c$ is
the speed of light, and ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$ are
the electric and magnetic fields, respectively.

Collisional interactions can be neglected when the time necessary for
the plasma to establish statistical equilibrium - the relaxation time
$\tau_{\rm rel}$ - is much greater than the characteristic time $\tau$
of the process being studied~\cite{klimon,Tigik2015}.
% The relaxation time of a plasma is defined
% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
% is the plasma parameter.

\section{Vlasov-Maxwell system of equations}
\label{vlasov-maxwell}
As mentioned before, in the absence of collisions, the plasma dynamics is given
by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
\end{eqnarray}
% here given in cgs units, as commonly used in the plasma physics literature.

In a statistical description, the charge density $\rho$
and the current density ${\bf J}$ depend on the velocity
distribution function
\begin{eqnarray}
  \label{qdensity}
    \rho({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v
    f_{\alpha}({\bf r},{\bf v},t)d^3v\\
\label{jdensity}
  {\bf J}({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
  f_{\alpha}({\bf r},{\bf v},t) d^3v,
\end{eqnarray}
where $\alpha$ accounts for all charged species that constitute
the plasma. In a fully ionized hydrogen plasma, $\alpha=i$ for
ions and $\alpha=e$ for electrons.

>>>>

Above, on the left-hand side, the differential vector operators $\nabla_{\bf r}$
and $\nabla_{\bf v}$ represent, respectively, the gradients in ($x,y,z$) space
and ($v_x, v_y,v_z$) velocity coordinates. The quantity ${\bf F}$ is the acting
force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
$\alpha$, which, in a fully ionized plasma, can assume two values: electrons
$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
variation of the velocity distribution function due to collisions between the
system's particles.

Collisional interactions are the central point of the present thesis.
However, the formalism presented in \Cref{noneigenmode}, departs from
the weak turbulence equations, which are the nonlinear approximation of
the kinetic equations for low-amplitude instabilities in a collisionless
plasma. The contribution of the correlations between \emph{source}
fluctuations, that account for collisional interactions  (see.~\cite{
  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
contribution in both wave and particle kinetic equations. The difference
of this new approach is that

%% ~\cite{klimon,Tigik2015}

\section{The Vlasov approach}
\label{vlasov-appro}
Collisional interactions can be neglected when the time necessary for
the plasma to establish statistical equilibrium is much greater than the
characteristic time of the process being studied. In this section, we
present a brief discussion about the necessary set of assumptions that
allow us to disregard the effect of collisions in dilute plasmas. In the
sequence we present the complete set of self-consistent equations for
a collisionless plasma.

% Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
% statistical equilibrium, i.e, the relaxation time.

the relaxation time $\tau_{\rm rel}$ 
% The relaxation time of a plasma is defined
% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
% is the plasma parameter.

As mentioned before, in the absence of collisions, the plasma dynamics is given
by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{\bf F}{m_{\alpha}}
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0.
\end{equation}

In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov},
is given by the Lorentz force added by an external force, which, at kinetic scales,
is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
following form
\begin{equation}
  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
  +{\bf F_{ext}},
  \label{florentz}
\end{equation}
where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, and $c$ is
the speed of light. The quantities ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$
are, respectively, the electric and magnetic fields, which are described by the
Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial {\bf B}}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
\end{eqnarray}

In a statistical description, the charge density $\rho$ and the current
density ${\bf J}$ depend on the velocity distribution function
\begin{eqnarray}
  \label{qdensity}
    \rho({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v
    f_{\alpha}({\bf r},{\bf v},t)d^3v\\
\label{jdensity}
  {\bf J}({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
  f_{\alpha}({\bf r},{\bf v},t) d^3v.
\end{eqnarray}
% where the fields are described by the Maxwell equations
% \begin{eqnarray}
%   \label{max1}
%   {\bf \nabla \cdot E}&=& 4\pi\rho\\
%   \label{max2}
%   {\bf \nabla \cdot B}&=& 0\\
%   \label{max3}
%     {\bf \nabla \times E}&=& -\frac{1}{c}
%    \frac{\partial {\bf B}}{\partial t}\\
%   \label{max4}
%     {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
%     +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
% \end{eqnarray}
% here given in cgs units, as commonly used in the plasma physics literature.

% In a statistical description, the charge density $\rho$
% and the current density ${\bf J}$ depend on the velocity
% distribution function
% \begin{eqnarray}
%   \label{qdensity}
%     \rho({\bf r},t)
%   &=&\sum_{\alpha}q_{\alpha}\int_v
%     f_{\alpha}({\bf r},{\bf v},t)d^3v\\
% \label{jdensity}
%   {\bf J}({\bf r},t)
%   &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
%   f_{\alpha}({\bf r},{\bf v},t) d^3v,
% \end{eqnarray}
% where $\alpha$ accounts for all charged species that constitute
% the plasma. In a fully ionized hydrogen plasma, $\alpha=i$ for
% ions and $\alpha=e$ for electrons.
